Formal Modeling and Verification of a Rate-Monotonic Scheduling Implementation with Real-Time Maude

### 2016-10-31 RMS/final-version/main.tex
modified a bit

%\documentclass[onecolumn]{IEEEtranTIE}
\documentclass[journal]{IEEEtranTIE}
\usepackage{graphicx}
\usepackage[noadjust]{cite}
\usepackage{picinpar}
\usepackage{amsmath}
\usepackage{stfloats}
%%\usepackage{dblfloatfix}
\usepackage{url}
\usepackage{flushend}
\usepackage[latin1]{inputenc}
\usepackage{colortbl}
\usepackage{soul}
\usepackage{multirow}
\usepackage{pifont}
\usepackage{color}
\usepackage{alltt}
\usepackage[hidelinks]{hyperref}
\usepackage{enumerate}
\usepackage{siunitx}
\usepackage{breakurl}
\usepackage{epstopdf}
\usepackage{pbox}

%% My packages
%% \usepackage[cmex10]{amsmath}
%% \interdisplaylinepenalty=2500
\usepackage{algpseudocode}
%% \usepackage{array}
\usepackage[caption=false,font=footnotesize]{subfig}

@@

    M. Zhou is with the School of Software, Tsinghua University,
    Beijing 100084, China (corresponding author; phone:
    +86-xxx-xxxx-xxxx; fax: xxx-xxxx-xxx; e-mail: zhoumin@gmail.com).

@@

A simple example showing this algorithm is depicted in
Fig.~\ref{f:example}(a). However in this paper, we consider an
implementation instead of the RMS algorithm itself, thus the model
would be more complicated than this standard, ideal
setting. Assumption~(A1) will be modified because of the interrupt
mask mechanism, while (A4) is relaxed to obtain a more realistic
analysis model.

@@

\subsubsection{Specification}
Real-Time Maude models systems as \emph{modules}. A module specifies a
\emph{real-time rewrite theory} ${\cal R} = (\Sigma, E\cup A ,
\mathit{IR}, \mathit{TR})$, where:
\begin{itemize}
\item $\Sigma$ is an algebraic \emph{signature}, that is, a set of
  declarations of \emph{sorts}, \emph{subsorts} and \emph{function
    symbols}. The function symbols are allowed to be mixfix, in which
  case underscores ``\verb|_|'' indicate the positions of parameters.
  \emph{Terms} are expressions built from function symbols and
  variables.
\item $(\Sigma, E\cup A)$ is a \emph{membership equational logic
  theory}, with $E$ a set of \emph{conditional equations} and
  \emph{memberships} on $\Sigma$, and $A$ a set of equational axioms
  such as associativity, commutativity and identity.  $(\Sigma, E\cup
  A)$ models the system's ``static'' states as terms of some sort, and
  is equipped with a built-in specification of a sort \verb|Time|.
\item $\mathit{IR}$ is a set of \emph{labeled conditional rewrite
  rules} specifying the system's local transitions. Each rule has the
  form $[l]~:~t\rightarrow t'\mbox{ \textbf{if}
  }\bigwedge^n_{j=1}cond_j$, where each $cond_j$ is an equality
  $u_j=v_j$, and $l$ is a \emph{label}, $t,t',u_j,v_j$ are terms. Such
  a rule specifies an \emph{instantaneous transition}, without
  consuming time, from an instance of $t$ to the corresponding
  instance of $t'$, \emph{provided} the conditions hold.
\item $\mathit{TR}$ is a set of (\emph{labeled}) \emph{tick rules} of
  the form $[l]~:~\{s\}\rightarrow\{s'\} \mbox{\textbf{ in time}
  }r\mbox{ \textbf{if} }cond$ that specify \emph{timed
    transitions}. Each tick rule advances time by $r$ time units from
  the \emph{entire} state modeled by term $s$ to the destination state
  $s'$.
\end{itemize}

$\mathit{IR}$ and $\mathit{TR}$ together model the ``dynamic''
behaviors of the system.

>>>>

%\documentclass[onecolumn]{IEEEtranTIE}
\documentclass[journal]{IEEEtranTIE}
\usepackage{graphicx}
\usepackage[noadjust]{cite}
\usepackage{picinpar}
\usepackage{amsmath}
\usepackage{stfloats}
\usepackage{url}
\usepackage{flushend}
\usepackage[latin1]{inputenc}
\usepackage{colortbl}
\usepackage{soul}
\usepackage{multirow}
\usepackage{pifont}
\usepackage{color}
\usepackage{alltt}
\usepackage[hidelinks]{hyperref}
\usepackage{enumerate}
\usepackage{siunitx}
\usepackage{breakurl}
\usepackage{epstopdf}
\usepackage{pbox}

%% My packages
%% \usepackage[cmex10]{amsmath}
%% \interdisplaylinepenalty=2500
\usepackage{algpseudocode}
%% \usepackage{array}
%%\usepackage{dblfloatfix}
%%\usepackage[caption=false,font=footnotesize]{subfig}

@@

    M. Zhou is with the School of Software, Tsinghua University,
    Beijing 100084, China (corresponding author; phone:
    +86-10-6277-3275; fax: +86-10-6278-3549; e-mail: zhoumin03@gmail.com).

@@

A simple example showing this algorithm is depicted in
Fig.~\ref{f:example}(a). However in this paper, we consider an
implementation instead of the RMS algorithm itself, thus the model
would be more complicated than this standard, ideal setting.
%% Assumption
(A1) will be modified because of the interrupt mask
mechanism, while (A4) is relaxed to obtain a more realistic analysis
model.

@@

\subsubsection{Specification}
Real-Time Maude models systems as \emph{modules}. A module specifies a
\emph{real-time rewrite theory} $\mathcal{R} = (\Sigma,
\mathit{E}\cup\mathit{A} , \mathit{IR}, \mathit{TR})$, where:
\begin{itemize}
\item $\Sigma$ is an algebraic \emph{signature}, that is, a set of
  declarations of \emph{sorts}, \emph{subsorts} and \emph{function
    symbols}. The function symbols are allowed to be mixfix, in which
  case underscores ``\verb|_|'' indicate the positions of parameters.
  \emph{Terms} are expressions built from function symbols and
  variables.
\item $(\Sigma, \mathit{E}\cup\mathit{A})$ is a \emph{membership
  equational logic theory}, with $\mathit{E}$ a set of
  \emph{conditional equations} and \emph{memberships} on $\Sigma$, and
  $\mathit{A}$ a set of equational axioms such as associativity,
  commutativity and identity.  $(\Sigma, \mathit{E}\cup\mathit{A})$
  models the system's ``static'' states as terms of some sort, and is
  equipped with a built-in specification of a sort \verb|Time|.
\item $\mathit{IR}$ is a set of \emph{labeled conditional rewrite
  rules} specifying the system's local transitions. Each rule has the
  form $[l]~:~t\rightarrow t'\mbox{ \textbf{if}
  }\bigwedge^n_{j=1}cond_j$, where each $cond_j$ is an equality
  $u_j=v_j$, and $l$ is a \emph{label}, $t,t',u_j,v_j$ are terms. Such
  a rule specifies an \emph{instantaneous transition}, without
  consuming time, from an instance of $t$ to the corresponding
  instance of $t'$, \emph{provided} the conditions hold.
\item $\mathit{TR}$ is a set of \emph{(labeled) tick rules} of
  the form $[l]~:~\{s\}\rightarrow\{s'\} \mbox{\textbf{ in time}
  }r\mbox{ \textbf{if} }cond$ that specify \emph{timed
    transitions}. Each tick rule advances time by $r$ time units from
  the \emph{entire} state modeled by term $s$ to the destination state
  $s'$.
\end{itemize}
$\mathit{IR}$ and $\mathit{TR}$ together model the system's ``dynamic''
behaviors.
